Figures

### 2018-03-19 scripts/analysis.Rmd
adjust map dot size and scale labels
working version of table 2
include conny metric key

@@

```{r maps, echo=FALSE, fig.cap="Map of lakes with low distance to nearest upstream lake at the NWS scale.", warning=FALSE, message=FALSE}

@@

>>>>

```{r table_2, echo=FALSE, fig.cap="Table 2"}

```{r table_3, echo=FALSE, fig.cap="Table 3"}

@@

```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions.", warning=FALSE, message=FALSE}

@@

```{r fig.cap="Connectivity metric box"}
knitr::include_graphics("../figures/conny_metric_key.pdf")
```
